% compiler: lualatex
% Preamble
\documentclass[DIV=13]{scrartcl}

% Packages
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tabularray}
\UseTblrLibrary{booktabs}
\usepackage{siunitx}
\usepackage{tabu}
\usepackage{graphicx}
\usepackage[expansion=false]{microtype}
\usepackage[sorting=none, maxbibnames=99, maxcitenames=2,backend=biber]{biblatex}
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}
\usepackage{csquotes}

\addbibresource{refs.bib}
\usepackage{symbols}

\setmainfont{Tempora}

% Document
\begin{document}
    \title{Rolling Process Variation Estimation Using a Monte-Carlo Method}
    \date{\today}
    \author{%
        M.~Weiner \thanks{Corresponding author}
        \and
        C.~Renzing
        \and
        J.~Mantel
        \and
        M.~Schmidtchen
        \and
        U.~Prahl
    }

    \extratitle{%
        \minisec{Max Weiner}
        max.weiner@imf.tu-freiberg.de\\
        Conceptualization, Methodology, Software, Formal analysis, Validation, Investigation, Writing - Original Draft\\
        Institute of Metals Forming, TU Bergakademie Freiberg

        \minisec{Christoph Renzing}
        christoph.renzing@imf.tu-freiberg.de\\
        Software, Validation, Investigation, Project administration, Writing - Review \& Editing\\
        Institute of Metals Forming, TU Bergakademie Freiberg

        \minisec{Jennifer Mantel}
        jennifer.mantel@imf.tu-freiberg.de\\
        Writing - Review \& Editing, Data curation\\
        Institute of Metals Forming, TU Bergakademie Freiberg

        \minisec{Matthias Schmidtchen}
        matthias.schmidtchen@imf.tu-freiberg.de\\
        Conceptualization, Supervision, Resources, Project administration, Writing - Review \& Editing\\
        Institute of Metals Forming, TU Bergakademie Freiberg

        \minisec{Ulrich Prahl}
        ulrich.prahl@imf.tu-freiberg.de\\
        Supervision, Resources, Writing - Review \& Editing\\
        Institute of Metals Forming, TU Bergakademie Freiberg

        \vfill

        \minisec{Funding}
        Not applicable.

        \minisec{Data Availability}
        Data openly available in a public repository that does not issue DOIs.
        Source code and data are available on GitHub at the following URLs:
        \begin{description}
            \item[Project Home] \url{https://github.com/pyroll-project}
            \item[Core Package] \url{https://github.com/pyroll-project/pyroll-core}
            \item[Benchmark Input and Data] \url{https://github.com/pyroll-project/pyroll-pub1-benchmark}
        \end{description}

        \minisec{Conflicts of Interest}
        The authors declare no conflicts of interest.

        \minisec{Acknowledgements}
        The authors thank Richard Pfeifer and Lukas Göschel for the preparation of the data.

        \minisec{Keywords}
        Rolling Simulation; Open Source; Groove Rolling
    }

    \maketitle

    \begin{abstract}
        Industrial processes are subject to uncertainties originating in variations of input material and process parameters,
        especially if manual treatment is involved.
        For hot rolling processes, in particular,
        variations in workpiece geometry and temperature are affecting the final product shape and material properties.
        In this work, a Monte-Carlo-Method is applied to a fast hot rolling model based on the open-source rolling simulation framework PyRolL for estimating and analysing the variational behaviour of an experimental semi-continuous rolling line for steel wire production.
        The effects of input tolerances and manual transport between the reversing passes on the final product properties are quantified.
        Crucial stages of the process in regard to product properties are identified
        The findings are compared with practical knowledge and experimental results of statistical rolling trials.
    \end{abstract}


    \section{Introduction}\label{sec:introduction}

    \input{sections/introduction}


    \section{Methods}\label{sec:methods}

    \input{sections/methods}


    \section{Results}\label{sec:results}

    \input{sections/results}


    \section{Summary and Outlook}\label{sec:summary}

    The method was found to give a good estimate of a rolling process' variational behaviour, however, dependent on the included influences and availability of statistical data that describe the input parameters.
    Uncertainties in input material were found to vanish along the process line, whereas uncertainties of the process itself were found to accumulate, which is in accordance with practical knowledge and intuition.
    A correlation was found between the size of the effect on a property, a process step applies, and its ability to depress already present uncertainties.
    Deviations in shape of the input workpiece were found to be equalized rapidly within a few passes.
    Deviations in temperature are reduced, but do not vanish.
    However, their actual impact on the microstructure was found to be negligible.

    The method offers a general way to investigate a process regarding the evolution of deviations and their impact on product properties.
    More reliable and convincing result could be obtained by use of more detailed and sophisticated model approaches, however, at the cost of a significant increase in computational effort.
    Additional influences and sources of deviation can be included in the analysis easily, since all uncertain inputs are processed in parallel.
    For each of them, a reasonable estimate of their statistical distribution must be available from data or educated guessing.
    Especially, the influence of modern process control systems is not included in the current model (as there were none present in the regarded experimental plant).
    Inclusion of static control behaviour is possible and required for industrial usage, as otherwise the deviation would be heavily overestimated.
    Dynamic behaviour can not be regarded with the current setup, since the used simulation procedure is stationary.
    Although, since the Monte-Carlo approach is agnostic regarding the core simulation procedure, the method is generally also applicable for this case, with a heavy increase in computational effort and the necessity to regard timeline results instead of scalar ones.
    The method does not include head and tail deviations, this has to be regarded separately.

    \input{sections/summary}

    \printbibliography

\end{document}
